---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753FALLsmit1666)
```


# Introduction
This package is a compilation of various packages used in MATH-4753. It includes 7 functions as well as 2 data files.

## The first function

get_mode receives a data set and returns the mode.

```{r}
getmode(ddt$DDT)
```

## The second function

mybin runs as many iterations as requested of a binomial trial and returns a plot.

```{r}
mybin(iter=1000, n=20, p=0.5)
```

## The third function

myboot2 applies the requested function to a data for iter iterations and creates a confidence interval using a bootstrap method of sampling, given alpha.

```{r}
myboot2(iter=10000, x=(c(2,3,4,5,4,2,2,6)), fun= "mean", alpha = 0.05)
```

## The fourth function

mycltu creates random unifrom distributions given the parameters and returns and creates a curve of the sample mean as well as a theoretical normal curve.

```{r}
mycltu(n=20, iter=1000)
```

## The fifth function

mymaxlik finds and returns that maximum likelihood of a function.

```{r}
logbin=function(x,param) log(dbinom(x,prob=param,size=10))
mymaxlik(x=c(4,6,7,6,5),param=seq(0,1,length=1000),lfun=logbin)
```

## The sixth function

myncurve returns a plot of the normal distribution given the parameters.

```{r}
myncurve(mu = 10, sigma = 5, a = 6)
```

## The first data set

The ddt data set contains data on fish species and the locations, including rivers, the samples were found.

```{r}
head(ddt)
```

## The second data set

The fire data set contains data on various fires, including the distance they travelled and the level of damage they caused.

```{r}
head(fire)
```

